---
title: "Assignment 7"
author: "Raja Alfiq Izrin"
date: "5/12/2020"
output: html_document
---

_Lab 6 - EDA_

<center>
<p style = "font-family:forte;font-size:55px">
__Exploring Data with R__
</center>
</p>

<font size= "5">
Determine what R function to use for the following:
1.	See basic descriptive statistics
```{r}
summary(attitude)
```
Run the function and observe the output, paste your output here.

a)	What is the difference between (attitude[4]) and (attitude$learning)
```{r}
attitude[4]
```
```{r}
attitude$learning
```
    The difference between (attitude[4]) and (attitude$learning) is that one is subsetting via index position and the other is subsetting using the variable name.

2.	Lists name of variables in a dataset
```{r}
names(attitude)
```

3.	Calculate number of rows in a dataset
```{r}
dim(attitude)[1]
```

4.	Calculate number of columns in a dataset
```{r}
dim(attitude)[2]
```

5.	List structure of a dataset
```{r}
str(attitude)
```

6.	See first 6 rows (by default) of dataset
```{r}
head(attitude)
```

7.	See first n rows of dataset
    head(attitude, n)
Select to see the first 15 rows of dataset
```{r}
head(attitude, n=15)
```
8.	See all rows but not the last row
```{r}
head(attitude, n=-1)
```

9.	See last 6 rows (by default) of a dataset
```{r}
tail(attitude)
```

10.	See last n rows of dataset
    tail(attitude, n)
Select to see the last 12 rows of dataset.
```{r}
tail(attitude, n=12)
```

11.	See the last n rows but not the first row
```{r}
tail(attitude, n=-1)
```

12.	Number of missing values
Which function will returns number of missing values in each variable of a dataset?
```{r}
sapply(attitude, function(attitude) sum(is.na(attitude)))
```

13.	Number of missing values in a single variable
```{r}
sum(is.na(attitude$privileges))
```

14.	Plot a simple graph, which will appear on a screen device.
```{r}
plot(attitude)
```

15.	Plot the graph shown below, and make it appear on a file device (a pdf file)
```{r}
with(attitude, (plot(privileges, learning, main="Learning Attitude", xlab = "Privileges", ylab = "Learning")))
```
```{r}
pdf(file="LearningAttitudeGraph.pdf")
with(attitude, plot(privileges, learning, main="Learning Attitude"))
dev.off()
```